Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-31 ms.tex
Thermally unstable solutions marked in table.
fixed results

Our numerical results, summarized in Table \ref{table:models}, allow us to study a range of CNM properties and to assess the validity of the analytic estimates from the previous section.  Cases for which $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|< 1$ at the stagnation radius are marked as `thermally unstable', as are cases for which the stagnation radius diverges and hence could not be resolved, resulting in their calculations being terminated.

@@

Figure~\ref{fig:stag} shows our results for the stagnation radius
$r_{\rm s}$, expressed in ratio to sphere of influence radius $r_{\rm
  soi}$, with different colors showing different values of $v_{w}$.
Cusp and core galaxies are marked with square and triangles,
respectively.  Shown for comparison are our analytic results
(eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core
galaxies, respectively, calculated assuming $\densSlope = 1$ and
$\densSlope= 0.6$, respectively (eq.~[\ref{eq:densSlope}]).  Our analytic estimates are found to
provide accurate fits to the numerical results for $v_{\rm w} \gtrsim
\sigma$, but the assumptions leading to these estimates become invalid
for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
For $v_{w} \gg \sigma$ the ratio $\rs/\rsoi$ does not depend
sensitively on break radius $r_{b}$, but the latter has a greater
influence when $v_{w} \lesssim \sigma$.  The three green squares which
are vertically aligned at the same value of $v_{w}/\sigma$ (close to
where the analytic estimate diverges) correspond to models with the
same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w =
300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $
50, 100, and 400 pc (from top to bottom).  As $r_{\rm b} \rightarrow
r_{s}$, the effects of the break radius is to the push the stagnation
radius inwards, decreasing the SMBH accretion rate.

>>>>

Our numerical results, summarized in Table \ref{table:models}, allow us to study a range of CNM properties and to assess the validity of the analytic estimates from the previous section.  Cases for which $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|< 10$ {\bf BDM: correct?} at the stagnation radius are marked as `thermally unstable', as are cases for which the stagnation radius diverges and hence could not be resolved, resulting in their calculations being terminated.

@@

Figure~\ref{fig:stag} shows our calculation of the stagnation radius $r_{\rm s}/r_{\rm
  soi}$, with different colors showing different values of $v_{w}$.
Cusp and core galaxies are marked with square and triangles,
respectively.  Shown for comparison are our analytic results
(eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core
galaxies, respectively, calculated assuming $\densSlope = 1$ and
$\densSlope= 0.6$, respectively (eq.~[\ref{eq:densSlope}]).

Our analytic estimates accurately reproduce the numerical results in the high heating limit $v_{\rm w} \gg
\sigma_0$ ($r_{\rm s} \lesssim r_{\rm soi}$).  However, for sufficiently low $v_{\rm w}/\sigma_0$ the stagnation radius exceeds the analytic estimate, approaching the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence occurs approximately when $\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0 < \zeta_c \propto (r_b/r_{\rm soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}], Appendix \ref{app:be}), and hence occurs at a higher value of $v_w/\sigma_0$ in the case of a core galaxies ($\Gamma = 0.8$) with large break radii.  This behavior explains the three core galaxies shown as green squares, which are vertically aligned at the same value of $v_{w}/\sigma$ (close to where the analytic estimate diverges) correspond to models with the same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w = 300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $ 50, 100, and 400 pc (from top to bottom).
